A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Muck around with spacing a bit
Tweak figure
Clean up a bit
Notation consistency
Lies
We've not spoken about null

      #2
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.3\linewidth}
      \centering Labelling of $G$
      \begin{tabular}[t]{cc}
      \hline
          Vertex & Label\\
      \hline
          #3
      \hline
      \end{tabular}
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.3\linewidth}
      \centering Labelling of $H$
      \begin{tabular}[t]{cc}
      \hline
          Vertex & Label\\
      \hline
          #4
      \hline
      \end{tabular}
  \end{minipage}
}

@@

\begin{figure}[ht]
\centering
    \includegraphics{graph_G}
    \includegraphics{graph_H}
%    \examplexG{}{}{}{}{}
%    \examplexH{}{}{}{}{}{}
\caption{Graphs $G$ and $H$}
\label{fig:alg1}
\end{figure}

@@

\begin{algorithm}[ht]
\DontPrintSemicolon
\nl $\FuncSty{expand}(\AlgVar{future},M)$ \;
\nl \Begin{
%\nl \lIf {$\AlgVar{future} = \emptyset$ \bf{and} $|M| > |\AlgVar{incumbent}|$}
\nl \lIf {$|M| > |\AlgVar{incumbent}|$}{$save(matching)$} \label{StoreIncumbent}
%\nl \lIf {$\AlgVar{future} = \emptyset$}{return}
\nl $bf \gets 0$ \label{SetBestFutureToZero} \;
\nl \lFor {$\langle P,T \rangle \in \AlgVar{future}$}{$\AlgVar{bf} \gets \AlgVar{bf} + \min(|P|,|T|)$}
\nl \lIf {$|M|  + \AlgVar{bf} \leq |\AlgVar{incumbent}|$}{return} \label{PruneSearch}
\bigskip
\nl $\langle P,T \rangle \gets \FuncSty{SelectLabelClass}(\AlgVar{future})$ \label{SelectClass} \;
\nl $v \gets \FuncSty{SelectVertex}(P)$ \label{SelectVertex} \;
\nl \For {$w \in T$ \label{WLoop}} {
\nl    $M \gets M \cup (v,w)$ \label{GrowM} \;
\nl    \bf{Let} $\AlgVar{future'} \gets \emptyset$ \label{NewFuture} \;
\nl    \For {$\langle P',T'\rangle \in future$ \label{InnerLoop}}{
\nl        \bf{Let} $P'' \gets P' \cap \N(G, v) \setminus \{v\}$ \label{NewPWithEdge} \;
\nl        \bf{Let} $T'' \gets T' \cap \N(H, w) \setminus \{w\}$ \;
\nl        \If {$P'' \neq \emptyset$ \bf{and} $T'' \neq \emptyset$}
        {$\AlgVar{future'} \gets \AlgVar{future'} + \langle P'' , T'' \rangle$ \label{AddToFutureWithEdge}}
\nl        \bf{Let} $P'' \gets P' \cap \invN(G, v) \setminus \{v\}$ \label{NewPWithoutEdge}  \;
\nl        \bf{Let} $T'' \gets T' \cap \invN(H, w) \setminus \{w\}$ \;
\nl        \If {$P'' \neq \emptyset$ \bf{and} $T'' \neq \emptyset$}
        {$\AlgVar{future'} \gets \AlgVar{future'} + \langle P'' , T'' \rangle$} \label{InnerLoopEnd}
       }
\nl   $\FuncSty{expand}(\AlgVar{future'},M)$ \label{ExpandWithV} \;
\nl   $M \gets M \setminus \{(v,w)\}$ \label{ShrinkM} \;
  }
\nl $P' \gets P \setminus \{v\}$ \label{RemoveV} \;
\nl $\AlgVar{future} \gets \AlgVar{future} \setminus \{\langle P,T \rangle\}$\;
\nl \lIf {$P' \neq \emptyset$} {$\AlgVar{future} \gets \AlgVar{future} \cup \{\langle P',T \rangle \}$}
\nl $\FuncSty{expand}(\AlgVar{future},M)$ \label{ExpandWithoutV} \;
}
\;
\nl $\FuncSty{McSplit}(G,H)$ \label{McSplitFun} \;
\nl \Begin{
\nl $\AlgVar{incumbent} \gets \emptyset$ \;
\nl $\FuncSty{expand}(\{\langle V(G),V(H) \rangle \},\emptyset)$ \label{FirstExpandCall} \;
\nl return $|\AlgVar{incubent}|$ \;
}
\caption{\McSplit\ algorithm for Maximum Common Subgraph}
\label{McCliqueAlg}
\end{algorithm}

@@

The remainder of $\FuncSty{expand}$ performs the search.  A label class
$\langle P, T \rangle$ is selected from $\AlgVar{future}$, where $P \subseteq V(G)$ and $T \subseteq V(H)$,
using some heuristic (\lineref{SelectClass}).  From this label class, a
vertex $v$ is selected from $P$ using a heuristic (\lineref{SelectVertex}). We now
iterate over all possible vertices in $T$ (\linerangeref{WLoop}{ShrinkM}). A
vertex $w \in T$ is selected and mapping $M$ is extended (\lineref{GrowM}). A
new set of label-classes, $\AlgVar{future'}$, is created (\lineref{NewFuture}).
Every label-class in $\AlgVar{future}$ can now be split
(\linerangeref{InnerLoop}{InnerLoopEnd}) into two new classes. The first of
these classes (\linerangeref{NewPWithEdge}{AddToFutureWithEdge}) contains
vertices in $P$ adjacent to $v$ and vertices in $T$ adjacent to $w$.  This is
added to $\AlgVar{future'}$ if both sets contain at least one vertex.  This is
then repeated symmetrically for non-adjacency
(\linerangeref{NewPWithoutEdge}{InnerLoopEnd}) using the compliments of the
graphs.  A recursive call is then made (\lineref{ExpandWithV}), on return from
which we remove the mapping $(v,w)$.  Having explored all possible mappings of
$v$ with vertices in $T$ we now consider what happens if $v$ is not matched
(\linerangeref{RemoveV}{ExpandWithoutV}). Note that removing $v$ from its label
class is equivalent to matching vertex $v$ to the null vertex $\bot$.

>>>>

      #2
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.3\linewidth}
      \centering Labelling of $G$
      \begin{tabular}[t]{cc}
      \hline
          Vertex & Label\\
      \hline
          #3
      \hline
      \end{tabular}
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.3\linewidth}
      \centering Labelling of $H$
      \begin{tabular}[t]{cc}
      \hline
          Vertex & Label\\
      \hline
          #4
      \hline
      \end{tabular}
      \medskip
  \end{minipage}
}

@@

\begin{figure}[t]
\centering
    \includegraphics{graph_G}
    \includegraphics{graph_H}
%    \examplexG{}{}{}{}{}
%    \examplexH{}{}{}{}{}{}
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}

@@

\begin{algorithm}[ht]
\DontPrintSemicolon
\nl $\FuncSty{expand}(\AlgVar{future},M)$ \;
\nl \Begin{
%\nl \lIf {$\AlgVar{future} = \emptyset$ \bf{and} $|M| > |\AlgVar{incumbent}|$}
\nl \lIf {$|M| > |\AlgVar{incumbent}|$}{$save(matching)$} \label{StoreIncumbent}
%\nl \lIf {$\AlgVar{future} = \emptyset$}{return}
\nl $bf \gets 0$ \label{SetBestFutureToZero} \;
\nl \lFor {$\langle P,T \rangle \in \AlgVar{future}$}{$\AlgVar{bf} \gets \AlgVar{bf} + \min(|P|,|T|)$}
\nl \lIf {$|M|  + \AlgVar{bf} \leq |\AlgVar{incumbent}|$}{return} \label{PruneSearch}
\medskip
\nl $\langle P,T \rangle \gets \FuncSty{SelectLabelClass}(\AlgVar{future})$ \label{SelectClass} \;
\nl $v \gets \FuncSty{SelectVertex}(P)$ \label{SelectVertex} \;
\nl \For {$w \in T$ \label{WLoop}} {
    \nl    $M \gets M \cup \{(v,w)\}$ \label{GrowM} \;
\nl    \bf{Let} $\AlgVar{future'} \gets \emptyset$ \label{NewFuture} \;
\nl    \For {$\langle P',T'\rangle \in future$ \label{InnerLoop}}{
\nl        \bf{Let} $P'' \gets P' \cap \N(G, v) \setminus \{v\}$ \label{NewPWithEdge} \;
\nl        \bf{Let} $T'' \gets T' \cap \N(H, w) \setminus \{w\}$ \;
\nl        \If {$P'' \neq \emptyset$ \bf{and} $T'' \neq \emptyset$}{
\nl            $\AlgVar{future'} \gets \AlgVar{future'} + \langle P'' , T'' \rangle$ \label{AddToFutureWithEdge}}
\nl        \bf{Let} $P'' \gets P' \cap \invN(G, v) \setminus \{v\}$ \label{NewPWithoutEdge}  \;
\nl        \bf{Let} $T'' \gets T' \cap \invN(H, w) \setminus \{w\}$ \;
\nl        \If {$P'' \neq \emptyset$ \bf{and} $T'' \neq \emptyset$}{
\nl            $\AlgVar{future'} \gets \AlgVar{future'} + \langle P'' , T'' \rangle$} \label{InnerLoopEnd}
       }
\nl   $\FuncSty{expand}(\AlgVar{future'},M)$ \label{ExpandWithV} \;
\nl   $M \gets M \setminus \{(v,w)\}$ \label{ShrinkM} \;
  }
\nl $P' \gets P \setminus \{v\}$ \label{RemoveV} \;
\nl $\AlgVar{future} \gets \AlgVar{future} \setminus \{\langle P,T \rangle\}$\;
\nl \lIf {$P' \neq \emptyset$} {$\AlgVar{future} \gets \AlgVar{future} \cup \{\langle P',T \rangle \}$}
\nl $\FuncSty{expand}(\AlgVar{future},M)$ \label{ExpandWithoutV} \;
}
\;
\nl $\FuncSty{McSplit}(G,H)$ \label{McSplitFun} \;
\nl \Begin{
\nl $\AlgVar{incumbent} \gets \emptyset$ \;
\nl $\FuncSty{expand}(\{\langle V(G),V(H) \rangle \},\emptyset)$ \label{FirstExpandCall} \;
\nl return $|\AlgVar{incubent}|$ \;
}
\caption{\McSplit\ algorithm for Maximum Common Subgraph}
\label{McCliqueAlg}
\end{algorithm}

@@

The remainder of $\FuncSty{expand}$ performs the search.  A label class
$\langle P, T \rangle$ is selected from $\AlgVar{future}$, where $P \subseteq
V(G)$ and $T \subseteq V(H)$, using some heuristic (\lineref{SelectClass}).
From this label class, a vertex $v$ is selected from $P$ using a heuristic
(\lineref{SelectVertex}). We now iterate over all possible vertices in $T$
(\linerangeref{WLoop}{ShrinkM}). A vertex $w \in T$ is selected and mapping $M$
is extended (\lineref{GrowM}). A new set of label-classes, $\AlgVar{future'}$,
is created (\lineref{NewFuture}).  Every label-class in $\AlgVar{future}$ can
now be split (\linerangeref{InnerLoop}{InnerLoopEnd}) into two new classes. The
first of these classes (\linerangeref{NewPWithEdge}{AddToFutureWithEdge})
contains vertices in $P$ adjacent to $v$ and vertices in $T$ adjacent to $w$.
This is added to $\AlgVar{future'}$ if both sets contain at least one vertex.
This is then repeated symmetrically for non-adjacency
(\linerangeref{NewPWithoutEdge}{InnerLoopEnd}). A recursive call is then made
(\lineref{ExpandWithV}), on return from which we remove the mapping $(v,w)$.
Having explored all possible mappings of $v$ with vertices in $T$ we now
consider what happens if $v$ is not matched
(\linerangeref{RemoveV}{ExpandWithoutV}).
